---
title: "Weight of Fish"
author: "Danitza Nunez"
date: "11/16/2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
```

## Import fish CSV using the import function that LUZ found  



# Predicting Fish Weight

## Perch
```{r}
Fish = read.csv('Fish.csv')
Perch = filter(Fish, Species == 'Perch')
Perch = subset(Perch,select = -Species)
weightPerch =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Perch)
summary.lm(weightPerch)
```


### Best Models

The best two variables are height and weight.  


### Best Two regressor model



```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

The Adjusted R-squared for Perch is 0.9372. The only variables that make a difference in this case is the p-value. So the only significant coefficient that determines the fish weight is the height where the p-value is 0.0333 less than 0.05



## Pike

```{r}
Pike = filter(Fish, Species == 'Pike')
Pike = subset(Pike,select = -Species)
weightPike =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Pike)
summary.lm(weightPike)
```


### Best Models

The best two variables are length1 and Length3 .  


### Best Two regressor model


```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

## Roach

```{r}
Roach = filter(Fish, Species == 'Roach')
Roach = subset(Roach,select = -Species)
weightRoach =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Roach)
summary.lm(weightRoach)
```


### Best Models


The best two variables are width and Length3  


### Best Two regressor model

```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

## Final Summary Statements


In predicting fish weight we tested three variables, 