---
title: "Weight of Fish"
author: "Danitza Nunez"
date: "11/16/2022"  
output: 
  html_document:
    number_sections: true
    toc: true
    toc_depth: 5

 
    
---


```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library(leaps)
```

## Import fish CSV using the import function that LUZ found  



# Predicting Fish Weight

## Perch
```{r}
Fish = read.csv('Fish.csv')
Perch = filter(Fish, Species == 'Perch')
Perch = subset(Perch,select = -Species)
weightPerch =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Perch)
summary.lm(weightPerch)
```


### Best Models



### Best Two regressor model



```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

The Adjusted R-squared for Perch is 0.9372. The best two variables are height and weight.  


## Pike

```{r}
Pike = filter(Fish, Species == 'Pike')
Pike = subset(Pike,select = -Species)
weightPike =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Pike)
summary.lm(weightPike)
```


### Best Models




### Best Two regressor model


```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

In the Pike model the Adjusted R-squared:  0.9794. The best two variables are length1 and Length3 .  

## Roach

```{r}
Roach = filter(Fish, Species == 'Roach')
Roach = subset(Roach,select = -Species)
weightRoach =lm(Weight~Length1 + Length2 + Length3 + Height+ Width, data =Roach)
summary.lm(weightRoach)
```


### Best Models





### Best Two regressor model

```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
In the roach model the Adjusted R-squared is  0.821.The best two variables are width and Length3    

## Final Summary Statements


In predicting fish weight we tested three variables, Perch, Pike and Roach. The adjusted R-square for Perch is 0.9372, The adjusted R-square for Pike is 0.9794, and the adjusted R-square for Roach is 0.821. The Pike fish gives the best results in predicting the fish weight based on the variables given in the best two regressor model since it had the biggest adjusted R-square of 0.9794 making it the best fit.
